### 2015-07-26 ms-thesis/ver2/intro/ms-thesis-intro.tex
-

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/ise.csv',index_col='Date')
df['Adj Close'].head(1000).plot()
plt.hold(False)
plt.savefig('ms-thesis-intro_01.png')
plt.hold(False)
\end{minted}

@@

>>>>

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/dji.csv',index_col='Date')
df['Adj Close'].head(100).plot()
plt.hold(False)
plt.hold(False)
plt.savefig('ms-thesis-intro_01.png')
plt.hold(False)
\end{minted}

@@

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/ise.csv',index_col='Date')
df2 = df[df.index <'22-06-2000']
df2['Adj Close'].plot()
plt.hold(False)
plt.savefig('ms-thesis-intro_02.png')
plt.hold(False)
\end{minted}

\includegraphics[height=6cm]{ms-thesis-intro_02.png}
